XXXXX

### 2014-09-28 paper/paper1.tex
R-43-COMPARISONS-BASED-ON-DATATYPE

@@

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL-3}
\centering
\begin{tabular}{ll}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
R-98-CHECK-VALIDITY-OF-URIS & \\
R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
R-112-EXTENSIBLE-CONSTRAINTS & \\
R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
R-119-VALIDATION-ON-NAMED-GRAPHS & \\
R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
R-123-STATE & \\
R-125-RDF-SHAPE-CHECKING & ShEx \\
R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
R-134-SPECIFY-USAGE-OF-TERMS & \\
R-135-CONSTRAINT-LEVELS & \\
R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
R-166-RDF-STREAMING-VALIDATION & \\
R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
R-185-FEDERALIZED-RDF-VALIDATION & \\
R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
R-191-SHAPES-RELATED-TO-TYPES & \\
R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPIN \\
R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
\hr
\end{tabular}
\end{table}

>>>>

\subsubsection{R-41-STATISTICAL-COMPUTATIONS}

\begin{itemize}
  \item examples: average, mean, sum
	\item covering approaches: SPARQL, SPIN
\end{itemize}

\subsubsection{R-42-COMPUTATIONS-BASED-ON-DATATYPE}

\begin{itemize}
	\item covering approaches: -
\end{itemize}

\subsubsection{R-43-COMPARISONS-BASED-ON-DATATYPE}

\begin{itemize}
	\item covering approaches: DQTP, ShEx, SPARQL, SPIN
\end{itemize}

COMP Pattern \cite{Kontokostas2014}

Depending on the property semantics,
there are cases where two different literal values must have
a specific ordering with respect to an operator. 
P1 and P2 are the datatype properties we need to compare and 
OP is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=).

\begin{ex}
SELECT ?s WHERE { 
    ?s %%P1%% ?v1 .
    ?s %%P2%% ?v2 .
    FILTER ( ?v1 %%OP%% ?v2 ) }
\end{ex}

example bindings (DQTP):

\begin{ex}
1. dbo:deathDate before ‘<’ dbo:birthDate
2. dbo:releaseDate after ‘>’ dbo:latestReleaseDate
3. dbo:demolitionDate before ‘<’ dbo:buildingStartDate
\end{ex}

dbo:deathDate before ‘\textless’ dbo:birthDate

\begin{ex}
P1 => dbo:deathDate
P2 => dbo:birthDate
OP => <
\end{ex}

valid data:

\begin{ex}
:AlbertEinstein
    dbo:birthDate '1879-03-14'^^xsd:date ;
    dbo:deathDate '1955-04-18'^^xsd:date .
\end{ex}

invalid data:

\begin{ex}
:NeilArmstrong
    dbo:birthDate '2012-08-25'^^xsd:date ;
    dbo:deathDate '1930-08-05'^^xsd:date .
\end{ex}

\subsubsection{R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS}

\begin{itemize}
	\item covering approaches: SPARQL, SPIN
\end{itemize}

@@

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL-3}
\centering
\begin{tabular}{ll}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
R-98-CHECK-VALIDITY-OF-URIS & \\
R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
R-112-EXTENSIBLE-CONSTRAINTS & \\
R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
R-119-VALIDATION-ON-NAMED-GRAPHS & \\
R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
R-123-STATE & \\
R-125-RDF-SHAPE-CHECKING & ShEx \\
R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
R-134-SPECIFY-USAGE-OF-TERMS & \\
R-135-CONSTRAINT-LEVELS & \\
R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
R-166-RDF-STREAMING-VALIDATION & \\
R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
R-185-FEDERALIZED-RDF-VALIDATION & \\
R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
R-191-SHAPES-RELATED-TO-TYPES & \\
R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
\hr
\end{tabular}
\end{table}
